---
title: "HW4_kmg0122"
author: "Mingang Kim"
date: '2021 10 16 '
output:
  pdf_document:
    latex_engine: xelatex
---
# 1. 

# 2.

# 3.

```{r}
library(tidyverse)
library(dplyr)
library(knitr)
library("data.table")
```


### (a).
```{r}
#load data
data.3.a<-read.csv("https://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/ThicknessGauge.dat",
                   header=F, skip=2, sep = " ")

#allocated names to the column
colnames(data.3.a)<-c("index", c("a1","a2","b1","b2","c1","c2"))

#made temporary data to merge by row.
data.temp.1 <- data.3.a %>% select(index,contains("1")) %>% rename(a=a1, b=b1, c=c1)

#added to index because its index also starts with 1. 
data.temp.2 <- data.3.a %>% select(index,contains("2")) %>%
  rename(a=a2, b=b2, c=c2) %>% mutate(index=index+10)

dat.3.a <- bind_rows(data.temp.1, data.temp.2) %>%
  rename("Operator 1"=a,"Operator 2"= b, "Operator 3"=c)

kable(head(dat.3.a), caption="Wall Thickness")
kable(summary(dat.3.a), caption="Wall Thickness Summary")

#Draw box plot to compare each operator's distribution
boxplot(dat.3.a[,2:4], ylab = "Measurements of thickness",  sub="Box plot for wall thickness")
```
I used a box plot because it is a efficient way to describe and compare the distribution of each operators. 

### (b).
```{r}
data.3.b<-read.csv("https://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/BrainandBodyWeight.dat",
                   header=F, sep=" ", skip=1)

#rename each column because dplyr cannot road data when column name is duplicated.
colnames(data.3.b)<-paste(rep(c("Body_Wt","Brain_Wt"),3),c(1,1,2,2,3,3),sep="_")

#made temporary data to merge by row.
data.temp.1<-data.3.b %>% select(contains("1")) %>% 
  
  rename( Body_Wt=Body_Wt_1, Brain_Wt=Brain_Wt_1)
data.temp.2<-data.3.b %>% select(contains("2")) %>% 
  
  rename( Body_Wt=Body_Wt_2, Brain_Wt=Brain_Wt_2)
data.temp.3<-data.3.b %>% select(contains("3")) %>% 
  
  rename( Body_Wt=Body_Wt_3, Brain_Wt=Brain_Wt_3)

#bind data by row. bind_row merge data by row which have the
# same column name. And then omitted NA data.
dat.3.b<-bind_rows(data.temp.1,data.temp.2,data.temp.3) %>% na.omit()

kable(head(dat.3.b), caption="Body and Brain weight Data")
kable(summary(dat.3.b), caption="Summary")

#Draw scatter plot to see if there is any relationship between Body weight and Brain weight

plot(dat.3.b$Body_Wt, dat.3.b$Brain_Wt, xlab="Body Weight",
     ylab="Brain Weight", main="Scatter plot between Body weight and Brain weight")
```
Since there was NA values, I omitted them. I drew scatter plot to see if there is any relatioship between body weight and brain weight. In the plot, there are two outliers. It seems that the reason for this may be some problem in data unit.

### (c).
```{r}
data.3.c<-fread("http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/LongJumpData.dat", 
                sep=" ", fill=T, skip=1,
                col.names = c(paste0(rep(c("year", "Long_Jump"),4),c(1,1,2,2,3,3,4,4))))

#made temporary data to merge by row.
data.temp.1<-data.3.c %>% select(contains("1")) %>% 
  rename(year=year1, Long_Jump=Long_Jump1) %>%
  mutate(year=year+1900)
data.temp.2<-data.3.c %>% select(contains("2")) %>% 
  rename(year=year2, Long_Jump=Long_Jump2) %>%
  mutate(year=year+1900)
data.temp.3<-data.3.c %>% select(contains("3")) %>%
  rename(year=year3, Long_Jump=Long_Jump3) %>% 
  mutate(year=year+1900)
data.temp.4<-data.3.c %>% select(contains("4")) %>% 
  rename(year=year4, Long_Jump=Long_Jump4) %>%
  mutate(year=year+1900)

# data merge
dat.3.c<-bind_rows(data.temp.1,data.temp.2,data.temp.3, data.temp.4) 

# data summary
kable(summary(dat.3.c), caption="Summary")

#drop NA values
dat.3.c <- dat.3.c %>% na.omit()

kable(head(dat.3.c), caption="Body and Brain weight Data")

#check that NA values disappear 
kable(summary(dat.3.c), caption="Summary")

#scatter plot 
plot(dat.3.c$year, dat.3.c$Long_Jump, xlab="Year", 
     ylab="Long jump", main="Scatter plot between year and long jump")
```
I drew scatter plot to see if there is any relatioship between the year and long jump. It seems that as time goes, the performance of long jump increases. 

### (d).
```{r}
data.3.d<-fread("http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/tomato.dat")

data.temp.1 <- data.3.d[,c(1,2)] %>% separate(`10000`, c("y1", "y2", "y3"), sep=",") %>%
  mutate(Density=rep(10000,2))
data.temp.2 <- data.3.d[,c(1,3)] %>% separate(`20000`, c("y1", "y2", "y3"), sep=",") %>%
  mutate(Density=rep(20000,2))
data.temp.3 <- data.3.d[,c(1,4)] %>% separate(`30000`, c("y1", "y2", "y3"), sep=",") %>% 
  mutate(Density=rep(30000,2))

dat.3.d <-bind_rows(data.temp.1, data.temp.2, data.temp.3 )
dat.3.d <-dat.3.d %>% rename(variety=V1) %>% 
  gather(key="Try", value = "yields", y1, y2, y3) %>% select(-Try) 

#change yields to numeric variable
dat.3.d<-dat.3.d %>% mutate(yields=as.numeric(yields),
                            variety=as.factor(variety),
                            Density=as.factor(Density))

#print data
kable(head(dat.3.d), caption="Tomato yield")

#check summary
kable(summary(dat.3.d), caption="Summary")

#plot
dat.3.d %>% ggplot(aes(x=variety, y=yields, 
           group=Density,
           shape=Density,
           color=Density)) + 
           geom_point() + 
           ggtitle("Plot of yields of two different varieties") + 
           geom_point(position=position_jitter(h=0.1, w=0.2)) +
           facet_grid(~factor(Density)) 
```
I drew plot like above because I want to compare each variety's difference in yield depending on Density. It seems that Ife#1 :9	has better yield than PusaEarlyDwarf:9.

### (e).
```{r}
data.3.e<-fread("https://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/LarvaeControl.dat")

#add age colunm and rename number with treatment
data.temp.age1<-data.3.e[,c(1:6)] %>% rename(Trt1=`1`, Trt2=`2`, Trt3=`3`, Trt4=`4`, Trt5=`5`) %>% 
  mutate(age=rep(1,8))
data.temp.age2 <- data.3.e[,c(1,7:11)] %>%
  rename(Trt1=`	1`, Trt2=`2`, Trt3=`3`, Trt4=`4`, Trt5=`5`) %>% 
  mutate(age=rep(2,8))

#merge data
dat.3.e <- bind_rows(data.temp.age1, data.temp.age2) %>%
  
  gather(key="Treatment", value="Counts", Trt1, Trt2, Trt3, Trt4, Trt5) %>%
  mutate(Treatment=substring(Treatment,4), age=as.factor(age), Block=as.factor(Block))

#print data
kable(head(dat.3.e), caption="Larvae Counts")

#check summary
kable(summary(dat.3.e), caption="Summary")

#plot
dat.3.e %>% ggplot(aes(x=age, y=Counts, 
           group=Treatment,
           shape=Treatment,
           color=Treatment)) + 
           geom_point(position=position_jitter(h=0.1, w=0.2)) +
  ggtitle("Plots of Lavae Counts") +
           facet_grid(~Block)
```
I drew plot like above because I want to compare each age's difference in counts depending on Treatment. I drew plots for each block and used shape option for treatment. It seems that age two group has more counts than age one group.  Density. 
